Predicting Internet Path Dynamics and Performance with Machine Learning

### 2017-12-20 paper-tex/paper.tex
add lstm fig

	\subsection{Temporal Properties of the Data}
	We believe temporally adjacent routes and \texttt{traceroute} records of a path share some common network nodes, thus their behavior contain implicit dependencies in temporal domain. While the data are organized in the order of time, the original method ignored this property but regard them as independent instances, i.e., the prediction for the next time step only depends on the features of the present, but does not use information given by more previous time steps. This manner fails the original method to capture even the most naive temporal dependencies. Here we do not provide strict proofs of the temporal dependencies that lie in these routes but simply throw some light on the possibility of their existence.
	\begin{figure*} 	
		\includegraphics[width=0.22\textwidth]{fig/total_life_8} 
		\label{fig:3.1a}
		\includegraphics[width=0.22\textwidth]{fig/total_life_20}
		\label{fig:3.1b}
		\includegraphics[width=0.22\textwidth]{fig/total_life_21}
		\label{fig:3.1c}
		\includegraphics[width=0.22\textwidth]{fig/total_life_30}
		\label{fig:3.1d}

@@

	\subsection{Long Short-Term Memory}
	In order to leverage the prediction targets' character of temporal locality, we further use Long Short-Term Memory (LSTM) to do time series modeling. More formally, we take $t-1$ most recent \texttt{traceroute} measurements features $(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-2}},\mathbf{x_{t-1}})$and the current \texttt{traceroute} measurement feature $\mathbf{x_t}$ together as the input,i.e.,$\mathbf{X}=(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-1}},\mathbf{x_{t}})$ And the out put is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.
	Let $G_{\theta}(\mathbf{x_i},\mathbf{h_i})$ the $\theta$ parameterized LSTM, we have:
	\begin{equation}
	\mathbf{h_{i+1}}=G_{\theta}(\mathbf{x_i},\mathbf{h_i}),
	\end{equation}iteratively. and when we have the $\mathbf{h_{t}}$, we calculate our final prediction $\hat{y}$ by a fully connected layer with parameter $\mathbf{W}$:
	\begin{equation}
	\hat{y}=\mathbf{W}\cdot\mathbf{h_t},
	\end{equation}
	and the loss function is:
	\begin{equation}
	\mathcal{L}=\frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2.
	\end{equation}
	The training objective is to minimize $\mathcal{L}$.

@@

	%\begin{acks}
	%	TODO
	%\end{acks}

	\bibliographystyle{ACM-Reference-Format}
	\bibliography{test-bib}

>>>>

	\subsection{Temporal Properties of the Data}
	We believe temporally adjacent routes and \texttt{traceroute} records of a path share some common network nodes, thus their behavior contain implicit dependencies in temporal domain. While the data are organized in the order of time, the original method ignored this property but regard them as independent instances, i.e., the prediction for the next time step only depends on the features of the present, but does not use information given by more previous time steps. This manner fails the original method to capture even the most naive temporal dependencies. Here we do not provide strict proofs of the temporal dependencies that lie in these routes but simply throw some light on the possibility of their existence.
	\begin{figure}[t] 
		\includegraphics[width=0.3\textwidth]{fig/lstm.pdf} 
		\caption{Illustration for LSTM.} 
		\label{fig:lstm} 
	\end{figure}
	\begin{figure*} 	
		\includegraphics[width=0.22\textwidth]{fig/total_life_8} 
		\label{fig:3.1a}
		\includegraphics[width=0.22\textwidth]{fig/total_life_20}
		\label{fig:3.1b}
		\includegraphics[width=0.22\textwidth]{fig/total_life_21}
		\label{fig:3.1c}
		\includegraphics[width=0.22\textwidth]{fig/total_life_30}
		\label{fig:3.1d}

@@

	\subsection{Long Short-Term Memory}

	In order to leverage the prediction targets' character of temporal locality, we further use Long Short-Term Memory (LSTM) to do time series modeling. More formally, we take $t-1$ most recent \texttt{traceroute} measurements features $(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-2}},\mathbf{x_{t-1}})$and the current \texttt{traceroute} measurement feature $\mathbf{x_t}$ together as the input,i.e.,$\mathbf{X}=(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-1}},\mathbf{x_{t}})$ And the out put is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.
	Let $G_{\theta}(\mathbf{x_i},\mathbf{h_i})$ the $\theta$ parameterized LSTM, we have:
	\begin{equation}
	\mathbf{h_{i+1}}=G_{\theta}(\mathbf{x_i},\mathbf{h_i}),
	\end{equation}iteratively. and when we have the $\mathbf{h_{t}}$, we calculate our final prediction $\hat{y}$ by a fully connected layer with parameter $\mathbf{W}$:
	\begin{equation}
	\hat{y}=\mathbf{W}\cdot\mathbf{h_t},
	\end{equation}
	and the loss function is:
	\begin{equation}
	\mathcal{L}=\frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2.
	\end{equation}
	The training objective is to minimize $\mathcal{L}$. The LSTM we adopt is illustrated in \textbf{Fig.\ref{fig:lstm}}

@@

	\begin{acks}
		TODO
	\end{acks}

	\bibliographystyle{ACM-Reference-Format}
	\bibliography{bibliography}
